Appendix A: Model fitting and selection for tracking data

### 2020-09-08 appendixA/appendixA.Rmd
update

---
title: "Appendix A: Model fitting and selection for tracking data"
output:
  pdf_document:
    toc: true
bibliography: "../paper/mybibfile.bib"
---

@@

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

@@

The way we are fitting the data can be visualized as follows:

@@

```{r}
pop_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "grey", lwd = 1) +
  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.05) +
  labs(title = "Population") +
  theme_classic()

@@

```{r poplevel}

@@

>>>>

---
title: "Appendix A: Model fitting and selection for tracking data"
output:
  html_document:
      toc: true
bibliography: "../paper/mybibfile.bib"
---

@@

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

@@

The way we are fitting the data can be visualized as follows, where each curve represents the population, an individual, or a family group:

@@

```{r fig.width=10}
pop_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "grey", lwd = 1) +
  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.05) +
  labs(title = "Population") +
  theme_classic()

@@

```{r poplevel, eval = FALSE}

@@

# References
